---
title: "HW5"
author: "Ou Sha"
date: "2023-11-15"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
```

# Problem 1
```{r}
# import data
homi <- read.csv("./data/homicide-data.csv")
```
The raw data has `r nrow(homi)` observations, and `r ncol(homi)` variables, including the id representing the case, victim's name, race, age, and sex, the date and the location of the case, and the status of the case.

```{r}
# clean data 
homi <- homi|>
  # create city_state variable
  mutate(city_state = str_c(city, state, sep = ", "))|>
  mutate(reso = case_when(disposition == "Closed without arrest" ~ "unsolved",
                          disposition == "Open/No arrest"        ~ "unsolved",
                          disposition == "Closed by arrest"      ~ "solved"))|>
  filter(city_state != "Tulsa, AL")|>
  select(-city, - state, -disposition)
```

```{r}
# summarize within cities to obtain the total number of homicides and umber of unsolved homicides
num_homi <- homi|>
  group_by(city_state)|>
  summarise(total_homi = n(), unsolved = sum(reso == "unsolved"))
num_homi
```
```{r}
# use the prop.test function to estimate the proportion of homicides that are unsolved in Baltimore, md
md <- filter(num_homi, city_state == "Baltimore, MD")
md_test <- prop.test(pull(md, unsolved), pull(md, total_homi))
# save the output as an R object
save(md_test, file = "prop_test_result.RData")
# apply the broom::tidy to this object
md_test <- broom::tidy(md_test)
# pull the estimated proportion and confidence intervals
data.frame(city_state = "Baltimore, MD",
           estimated_prop = pull(md_test, estimate),
           confidence_interval = paste("(", pull(md_test, conf.low), ",",
                                       pull(md_test, conf.high), ")"))
```
```{r}
# run prop.test for each of the cities
result <- num_homi|>
  mutate(test = map2(unsolved, total_homi, \(x,y)prop.test(x,y)),
         tidy = map(test, broom::tidy))|>
  unnest(tidy)|>
  #extract both the proportion of unsolved homicides and the confidence interval for each
  select(city_state, estimate, conf.low, conf.high)
result
# create plot 
result|>
  # Organize cities according to the proportion of unsolved homicides
  ggplot(aes(x = estimate, y = reorder(city_state,estimate))) + 
  geom_point() + 
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high))+
  labs(x = "proportion of unsolved homicides", y = "location", title = "Estimates and CIs for each city")
```
Based on the plot, Richmond, VA has the smallest estimated proportion of unsolved homicides and Chicago, IL has the largest estimated proportion of unsolved homicides with a small CI. 

# Problem 2
```{r}
# create a tidy dataframe
p2 <- data.frame(name = list.files("./data/p2"), path= str_c("./data/p2/", list.files("./data/p2")))|>
  mutate(data = map(path, read.csv))|>
  unnest(c(data))|>
  separate(name, c("arm", "id"), "_")|>
  mutate(id = str_sub(id, start = 1, end = 2))|>
  select(-path)|>
  # switch from “wide” to “long” format
  pivot_longer(
    week_1:week_8,
    names_to = "week", 
    values_to = "observation")
# make spaghetti plot
p2|>
  ggplot(aes(x = week, y = observation, group = id, color = id)) +
  geom_line() +
  facet_grid(~arm)+
  labs(title = "observations on each subject over time",
       x = "week",
       y = "observations") +
  theme_minimal()
```
The control group exhibited fluctuations around a constant value, while the experimental group demonstrated an increasing trend as time progressed. 
